Handling String-Number Conversion in String Constraint Solving

### 2019-11-13 evaluation.tex
description to benchmarks

\paragraph{A Comparison with other tools on well-known benchmarks.}
In this group of benchmarks, we would like to show that the performance of our tools is not only comparable to the performance of other tools, but in many cases even better. This group of benchmarks consists of PyEx, APLAS, LeetCode, StringFuzz, cvc4\textsubscript{pred} and cvc4\textsubscript{term}, which are benchmarks that was created by others and that contain a very few formulae with constraints of string-number and number-string conversion.

The first benchmark is called PyEx according to the same-named tool, which is a symbolic executor designed for Python developers to achieve high-coverage testing. This benchmark was obtained from the CVC4 group who ran PyEx on a test suite from 4 popular Python packages: httplib2, pip, pymongo, and requests. PyEx benchmark consists of 25421 tests which contain formulae with diverse string constraints. Although this benchmark was created by cvc4 group and cvc4 solved more SAT cases than the other tools, z3-trau was behind by less than 1\textperthousand\ of cases and moreover managed to solve the most UNSAT cases.

>>>>

\paragraph{A Comparison with other tools on conversion-less benchmarks.}
This group of benchmarks consists of PyEx, APLAS, LeetCode, StringFuzz, cvc4\textsubscript{pred} and cvc4\textsubscript{term}, which are benchmarks that were obtained by using an existing tool or generated by other groups. In this group of benchmarks, we would like to show that the performance of our tools is not only comparable to the performance of other tools, but in some cases even better.

The first benchmark is called PyEx~\cite{pyex} according to the same-named tool, which is a symbolic executor designed for Python developers to achieve high-coverage testing. This benchmark was obtained from the CVC4 group who ran PyEx on a test suite from 4 popular Python packages: httplib2, pip, pymongo, and requests. PyEx benchmark consists of 25421 tests which contain formulae with diverse string constraints.

The second benchmark is called APLAS that was created by authors of \textsf{$Kepler_{22}$}~\cite{aplas}. The benchmark includes a total of 600 hand-drafted tests (298 satisfiable and 302 unsatisfiable) involving looping word equations (Both sides of the string equality have a common variable) and length constraints over strings.

The next benchmark is called LeetCode~\cite{LeetCode} that was obtained by extracting constraints from Python's testing solutions provided by LeetCode platform. They provide many programming examples and their solutions gathered from technical interviews for companies. Leetcode consists of 881 satisfiable and 1785 unsatisfiable tests that, like PyEx, contain diverse string constraints.

StringFuzz is our next bechmark that is named after a fuzzer~\cite{StringFuzz} for automatically generating SMT-LIB string constraints. We used StringFuzz to generate 1065 tests including word (dis)equalities, regular membership and arithmetic constraints.

The last two benchmarks, called $\text{cvc4}_{\text{pred}}$ and $\text{cvc4}_{\text{term}}$, are obtained from cvc4 group~\cite{termEQ}. This set of benchmarks consists of the verification of term equivalences over strings and includes various string constraints including string-number and number-string conversion constraints.
